% \documentclass[10pt,a4paper]{moderncv}                
%\usepackage[utf8]{inputenc}
% \usepackage[scale=0.85]{geometry}
\documentclass[11pt,a4paper]{moderncv}

%\usepackage[T1]{fontenc}      % Activer toutes les toucher du clavier
%\usepackage[francais]{babel}  % Langue Français

% moderncv themes
%\moderncvtheme[orange]{casual}         
\moderncvtheme[blue]{classic}        

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%
% adjust the page margins
\usepackage[top=1.5cm, bottom=1cm, left=1.5cm, right=1.5cm]{geometry}
%\usepackage{hyperref}
%\hypersetup{colorlinks=false}

%\recomputelengths                             % required when changes are made to page layout lengths

\usepackage{ifpdf}
\ifpdf
	\pdfinfo {
		/Author (Nicolas REY)
		/Title (Nicolas REY - Scala / Spark Developer - Big Data)
		% /Subject (SUBJECT)
		% /Keywords (KEYWORDS)
%		/CreationDate (D:20110109220854)
	}
\fi

%\addtolength{\oddsidemargin}{10pt}
%\addtolength{\textwidth}{0pt}
%\addtolength{\topmargin}{-05pt}
%\addtolength{\textheight}{10pt}
%\addtolength{\marginparsep}{0pt}
%\addtolength{\marginparwidth}{0pt}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\nopagenumbers{}	% uncomment to suppress automatic page numbering for CVs longer than one page


\firstname{Nicolas}
\familyname{Rey}
\title{Scala / Spark Developer - Big Data}
\address{74 rue Championnet}{75018 Paris}
\mobile{+33 6 26 09 05 07}
\email{n.rey@lateral-thoughts.com}
% \extrainfo{29 ans, Single, Permis voiture}


\begin{document}
\maketitle

\vspace{1cm}
\section{Education}
\cventry{March 2018}{Deep Learning Training}{University of Montreal}{}{Montreal}{
  \smallskip
  This one week training consisted in a big introduction to deep learnig, the mathematical concepts behind it,
as well as several practical works.
  \bigskip
}
\cventry{Sept. 2014}{Spark Training}{Lateral Thoughts}{}{Paris}{
  \smallskip
  \begin{itemize}
    \item Spark Core
    \item Spark SQL
    \item Spark Streaming
  \end{itemize}
  \bigskip
}
\cventry{2008 - 2012}{École Centrale de Nantes - Software engineering specialization}{Generalist engineering school}{}{}{
  The \textit{École Centrale de Nantes} is a well known French engineering school. It delivers a very wide ranging curriculum.
}

\vspace{0.5cm}
\section{Languages}
\cvlanguage{French}{Native}{}
\cvlanguage{English}{Fluent (ToEIC : 885)}{Working in English, internship in India (4 months), South-Africa (6 stays)}
\cvlanguage{Spainish}{Notions}{}
\cvlanguage{Russian}{Notions}{}

\vspace{0.5cm}
\section{IT skills}
\begin{tabular}{ll}
  \vspace{0.1cm}
  \hspace{0.1cm} Languages & \hspace{0.5cm} \textbf{Scala}, Java, JavaScript, Bash (basics) \\ \vspace{0.1cm}
  \hspace{0.1cm} Big Data ecosystem & \hspace{0.5cm} \textbf{Spark}, Kafka, HDFS, Cloudera \\ \vspace{0.1cm}
  \hspace{0.1cm} Scala ecosystem & \hspace{0.5cm} Play 2!, Akka (basics) \\ \vspace{0.1cm}
  \hspace{0.1cm} Code management & \hspace{0.5cm} SBT, Maven, Jenkins, Git, GitlabCI \\ \vspace{0.1cm}
  \hspace{0.1cm} Data bases & \hspace{0.5cm} Cassandra, MongoDB, HBase (basics) \\ \vspace{0.1cm}
  \hspace{0.1cm} System & \hspace{0.5cm} GNU/Linux, Ansible, Docker, Vagrant \\ \vspace{0.1cm}
  \hspace{0.1cm} Cloud Computing & \hspace{0.5cm} Microsoft Azure \\ \vspace{0.1cm}
\end{tabular}



\newpage
\section{Experiences}
% \cventry{}{}{}{}{}{}
\cventry{2018 - Today\\2012 - 2017\\6 years}{Scala/Java Software Engineer - Big Data}{Lateral Thoughts}{Paris}{}{
  \small Consultant specialized in \textbf{Scala}, \textbf{Spark} development, and Big Data ecosystems.
  \medskip
  \begin{itemize}
    \item Advise clients regarding their needs
    \item Implementing solutions using Scala, Spark, Kafka and other tools in the ecosystem
  \end{itemize}
  \medskip
  Lateral Thoughts is what we today call a "freedom-form company"
  \medskip
  \begin{itemize}
    \item No chief nor hierarchy. Fully self organized
    \item Great cooperation, emulation et mutual aid between employees
    \item An expertise in Scala, Spark, and Big Data development
  \end{itemize}
  \medskip
  \textbf{Environment :} \textit{\textbf{Scala}, \textbf{Spark}, Kafka, Cassandra, Hadoop, Scrum}
  \bigskip
}
\cventry{2018 - Today\\8 months}{Scala/Spark Software Engineer - Big Data}{Renault Digital}{Paris}{France}{
  \small Development of a tool to trace parts, components and costs of cars with Scala and Spark. \\
  \medskip
  \begin{itemize}
    \item Advising about the architecture and technical solutions
    \item Implementation of the data processing using Scala / Spark (about 3 TB of volume)
    \item Data storage in HDFS, ElasticSearch and HBase
    \item Implementation of the APIs to expose our data using Scala / Play2!
    \item Practice of Test Driven Development (TDD)
    \item Devops role aswell to improve deployment, scheduling, code quality and monitoring of our apps
  \end{itemize}
  \medskip
  \textbf{Environment :} \textit{\textbf{Scala}, \textbf{Spark}, HBase, ElasticSearch, HDP} \\
  \textbf{Company :} \textit{Renault Digital is a subsidiary of the Renault group gathering digital projects}
  \bigskip
}
\cventry{2017 - 2018\\11 months}{Scala/Spark Advisor - Big Data}{agileDSS}{Montréal}{Canada}{
  \small \textbf{Scala / Spark / Big Data} advisor. \\
  I also gave two sessions of Spark Core training at Microsoft.
  \medbreak
  For my clients, my role consisted in :
  \medskip
  \begin{itemize}
    \item Helping them in the design of their Big Data architecture
    \item Implementing using Scala / Spark
    \item Strict practice of Test Driven Development (TDD)
    \item Training their employees in Scala, Spark, and the Big Data ecosystem
  \end{itemize}
  \medskip
  For the agency, mon role consisted in :
  \medskip
  \begin{itemize}
    \item Getting involved in the development of the Big Data practice
    \item Choosing the Big Data technology of reference
    \item Running most of the technical recruitment interviews
    \item Training employees to the Big Data practice and technologies
  \end{itemize}
  \medskip
  I have mostly worked with with Microsoft because of clients' choices.
  \medbreak
  \textbf{Environment :} \textit{\textbf{Scala}, \textbf{Spark}, Microsoft Azure} \\
  \textbf{Company :} \textit{AgileDSS is IT services company specialized in BI and advise around data}
  \bigskip
}
\cventry{2016 - 2017\\7 months}{Scala/Spark Software Engineer - Big Data}{Pages Jaunes}{Paris}{}{
  \small Redesign the applications regarding audience data of Pages Jaunes with Spark
  \medskip
  \begin{itemize}
    \item Development of several applications to ingest and valorize data
    \item Building the software factory (Jenkins, Sonatype Nexus)
    \item DevOps : deployment  with Ansible, pipeline of jobs with Jenkins
    \item Training the team to Scala, Spark, and to work with Agile methods
  \end{itemize}
  \medskip
  \textbf{Environment :} \textit{\textbf{Scala}, \textbf{Spark}, HDFS, Cloudera, Avro, Parquet} \\
  \textbf{Project management :} \textit{Agile methods} \\
  \textbf{Company :} \textit{Pages Jaunes is a search engine of professionals. About 5 millions daily users.}
  \bigskip
}
\cventry{2015 - 2016\\10 months}{Scala Software Engineer - Big Data}{Carrefour}{Paris}{}{
  \small Development of the real time data lake for Carrefour
  \medskip
  \begin{itemize}
    \item Ingestion in Kafka of multiple data sources
    \item Computing the data with Spark Streaming
    \item Normalizing the data in avro format
    \item Storage of the data in HDFS and Cassandra
    \item Development of APIs with Spray to access the data
    \item The platform was splitted between a Mesos cluster and a Cloudera cluster
  \end{itemize}
  \medskip
  \textbf{Environment :} \textit{\textbf{Scala}, \textbf{Spark}, Mesos, Akka, Cassandra, Kafka, HDFS, Cloudera, Spray, Avro} \\
  \textbf{Company :} \textit{Carrefour is a major big distribution company. 5600 retail stores in France.}
  \bigskip
}
\cventry{2014 - 2015\\1 year}{Scala/Java Software Engineer}{Vidal}{Paris}{}{
	\small Software development for the medical drug industry
	\medskip
  \begin{itemize}
    \item Development of a tool in Scala and Akka to manage updates of a heavy client
    \item Development of HATEOAS RESTful APIs on a medical database
    \item Development of a BDD testing project with Cucumber
  \end{itemize}
  \medskip
  \textbf{Environment :} \textit{Scala, Java, Akka, Guava, Spring, Hibernate, Cucumber, Github, Docker} \\
  \textbf{Gestion de projet :} \textit{Agile methods / Scrum} \\
  \textbf{Company :} \textit{Vidal is the French leader of medical drug data.}
  \bigskip
}
\cventry{2014\\9 months}{Java Software Engineer}{SACEM}{Paris}{}{
	\small Redesign of several declaration and payment web sites
	\medskip
  \begin{itemize}
    \item Backend development in Java and Spring. Heavy use of Guava.
    \item Frontend development in JavaScript and ReactJS
    \item Interface testing with Fluentlenium
    \item Development of a tool with RabbitMQ in order to handle the underlying database unavailability
    \item Use of Git and Jenkins for code management
  \end{itemize}
  \medskip
  \textbf{Backend Environment :} \textit{Java, Guava, Spring, Fluentlenium} \\
  \textbf{Frontend Environment :} \textit{JavaScript, ReactJS} \\
  \textbf{Gestion de projet :} \textit{Agile methods / Scrum} \\
  \textbf{Company :} \textit{SACEM is the company in charge of collecting and redistributing music copyrights in France.}
  \bigskip
}
\cventry{2013\\7 months}{Scala Software Engineer}{FONTYOU}{Paris}{}{
	\small Development of a web application dealing with font co-creation
	\medskip
  \begin{itemize}
    \item Development of the APIs with Scala, Play2!, MongoDB
    \item Development of the frontend with JavaScript, BackboneJS, CSS3
    \item System administration of the software factory and the production environment
    \item Development of a proof of concept for vectorial drawing inside a browser
  \end{itemize}
  \medskip
  \textbf{Backend Environment :} \textit{\textbf{Scala}, Play2!, MongoDB, Zabbix} \\
  \textbf{Frontend Environment :} \textit{JavaScript, BackboneJS, RequireJS, HTML5/CSS3, LessCSS} \\
  \textbf{Gestion de projet :} \textit{Agile / Scrum} \\
  \textbf{Company :} \textit{Fontyou is a startup which at the time was working on a social network of font co-creation.}
  \bigskip
}
% \cventry{}{References on demand}{}{}{}{}
% \cventry{2012 - 2013\\7 months}{Ingénieur Développeur Scala}{Vidal}{Paris}{}{
% 	\small Développement d'un client lourd
% 	\medskip
%   \begin{itemize}
%     \item Développement d'un système de notification installé chez les clients
%     \item Gestion de l'expiration et du renouvellement de la license des clients
%   \end{itemize}
%   \medskip
%   \textbf{Environnement :} \textit{\textbf{Scala}, Akka, SWT, JavaScript, HTML/CSS} \\
%   \textbf{Gestion de projet :} \textit{Agile / Scrum}
%   \bigskip
% }
% \cventry{Nov. 2012\\1 months}{Développement d'APIs REST HATEOAS}{Vidal}{Paris}{}{
% 	Java, Spring, Hibernate, protocole ATOM. TDD avec JUnit, Mockito.\\
% 	Méthodes AGILE : SCRUM.
% }
% \cventry{Avril - Sept. 2012\\6 months}{Stage de fin d'études - Développement Web/Mobile}{Eklaweb}{Nantes}{}{
%   Développement d'applications mobiles HTML5 avec Backbone.js.\\
%   Serveur : Scala, Unfiltered, Play2!, MongoDB, PostgreSQL.\\
%   Article sur le blog technique d'Eklaweb : "Gestion des dates en informatique".
% }
% \cventry{Mai à août 2011\\4 months}{Stage ingénieur en développement mobile}{Amadeus}{Bangalore}{Inde}{
%   Application iPad pour valider la maturité du développement mobile HTML5.\\
%   Utilisation importante de JavaScript (jQuery), PhoneGap, HTML5, CSS3 et SQLite.\\
%   Web scraping d'un site avec un script Python.
% }
% \cventry{Février à avril 2011}{Application Android de simulation mécanique}{Institut de recherche en Génie Mécanique}{Nantes}{}{Hautes performances nécessaires. Java, OpenGL ES, Bibliothèque de calcul matriciel (EJML).}
%\cventry{}{}{}{}{}{}


\newpage
\section{Personal projects}
\cventry{2019}{Spark Tools}{}{}{}{
  \small Development of a SourceManager to abstract the reading/writing of sources and the creation of a Hive table. Adds several very useful SaveMode.
  \bigskip
}
\cventry{2019}{Slack Notifier for Yarn projects}{}{}{}{
  \small Development of a simple notification tool implementing the Slack Incoming Webhooks API, and specialized to post status of applications.
  \bigskip
}
\cventry{2017}{Docker image for TaigaIO}{}{}{}{
  \small Creation of a Docker image for the \textit{taiga.io} software. TaigaIO is a simplified tool for task management oriented to Agile methods.
  \bigskip
}
\cventry{2017}{Docker image for Azkaban}{}{}{}{
  \small Creatiof of a Docker image for the \textit{Azkaban} software. Azkaban is a workflow manager developed by LinkedIn.
  \bigskip
}
\cventry{2015}{Personal Server}{}{}{}{
  \small Installation of a development server with Ansible \\
  \textit{Ansible, Nginx, OwnCloud, GitLab, Linux Debian}
  \bigskip
}
\cventry{2015}{Personal Computer}{}{}{}{
  \small Automation of the install and configuration of my own personal computers with Ansible
}

\vspace{0.5cm}
\section{Interests}
\cvline{IT}{Free and open source softwares, functionnal programming.}
\cvline{Hobbies}{Salsa and other danses, Paragliding, Photography, Geopolitics, Good food.}
\cvline{Travels}{17 years in Libreville (Gabon), Road trips in Europe (11 countries), 4 months in India.}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\end{document}
